
# Computational Genomics with R HW1
#### Name: Thomas Brew


### Section 2.10.1

```{r} 

#Problem 1
2+3

#Problem 2
sqrt(36)

#Problem 3
log10(1000)

#Problem 4
log2(32)

#Problem 5
y=2+3+4
y

#Problem 6
abs(5-145)

#Problem 7
x=sqrt(625)/5
x
# Problem 8

x=x*5
x



```


### Section 2.10.1

```{r}
#For some reason there is no problem 9 in the book

#Problem 10
vecA=c(1,2,3,5,10)
vecA
#Problem 11
length(vecA)

# Problem 12
vec=2:15
vec
#Problem 13
vec=rep(4,10)
vec

#Problem 14
vec=c(TRUE,TRUE,FALSE,TRUE)
vec

#Problem 15
vec=c("PAX6","ZIC2","OCT4","SOX2")
vec
#Problem 16
x=vec[6]
y=vec[5]
x
y # I am not sure which vector it wants to index but the one from the previous question has 4. 
x=vecA[5]
y=vecA[6]
x
y

# Problem 17
myvec=1:5
myvec[c(TRUE,TRUE,FALSE,FALSE,FALSE)]
myvec[c(TRUE,TRUE,FALSE,FALSE,TRUE)]

#Problem 18
myvec>3
myvec==4
myvec<=2
myvec!=4

#Problem 19
myvec[myvec>2]

#Problem 20
mat1=matrix(1:15,nrow=5,ncol=3)
#Problem 21
mat1=matrix(1:15,nrow=5,ncol=3,byrow=TRUE)

```
Probelm 21:
when a matrix takes c initially fills out the matrix by taking the elements of the matrix and filling out the
first column. Then all following columns until they are all filled.
The byrow instead fills out by filling out across the row first.

```{r}
# Problem 22
#I used the byrow matrix
mat1[1:3,1:3]

#Problem 23
mat1[4:5,1:3]

#Problem 24
cmat=mat1[1:5,1:2]
cmat
class(cmat)
# problem 25
cmat=mat1[1:5,1]
cmat
class(cmat)
```
The first one had class matrix, array.
This second one had class Integer
